---
title: "Lab 00 - Hello IDS!"
author: "Toby Craik"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Magnus", "Ben", "Stewart", 
           "Sophie", "Toby"),
  github_username = c("MagnusBryce", "BWipat", "stewart620", 
                      "username", "tobycraik"), 
  colour = c("blue", "royalblue", "blue", 
             "purple", "blue"),
  hobby = c("swimming", "climbing", "running", 
            "sleeping", "running"),
  favourite_number = c(8, 15, 6, 3, 4)
  )

team_data
```

### Exercise 18

We now work on visualising our data.

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

The bar chart shows everyone's favourite number in descending order filled with their favourite colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub username", 
          y = "Favourite number",
          title = "Favourite colours and numbers")
```

labs() provides the labels for the axes on the chart.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

A pie chart might be more useful as this would show the proportion of people with each hobby.
